---
title       : Crime in the USA from 1960 to 2000
subtitle    : Animated Longitudinal View in a Slidify Presentation 
author      : Radu Craioveanu
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap,quiz,shiny,interactive] # {mathjax, quiz, bootstrap}
ext_widgets: {rCharts: [libraries/nvd3]}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Project Objective

1. Provide a longitudinal animated view of the crime rate in USA
2. Showcase the work as a Shiny App and load on the RStudio Shiny server 
3. Document the work via a Slidify presentation
4. Push all the work to a Github repo

--- .class #id 

## The Application

1. Provides crime data in the USA from 1960 to 2000
2. The crime data is categorized as Low, Medium and High
3. There is a slider input that allows selection of a decade year
4. The slider also has a run mode, set to 2.5 seconds per decade
5. Shiny server app URL for CrimeUSA 
https://radunh.shinyapps.io/CrimeUSAShiny
6. Github project URL for CrimeUSA Shiny app
https://github.com/radunh/DevelopingDataProducts/tree/master/CrimeUSA/CrimeUSAShiny
7. Github project URL for CrimeUSA Slidify preso 
http://radunh.github.io/DevelopingDataProducts

--- .class #id 

## Interactive Chart - ShinyUI

#```{r, echo = F, opts.label='shiny', message=FALSE, eval=FALSE, cache=FALSE}
require(rCharts)
shinyUI(bootstrapPage(
  div(class="row",
      div(class="span4",
          sliderInput("Decade","", min=1960, max=2000, value=1960,  format="###0",step=10,animate=animationOptions(loop=T, interval=2500)))),

  htmlOutput("decade"),
  img(src = "legend.png", height = 40, width = 200),
  showOutput("animatedChart","datamaps")
  ))
#```

--- .class #id 

## Interactive Chart - ShinyServer

#```{r, echo = F, opts.label='shiny', message=FALSE, eval=FALSE}
## Load libraries
library(rCharts)
library(shiny)
library(plyr)

## Set working directory
setwd('~/OneDrive/Radu Craioveanu/School/Data Science at John Hopkins on Coursera/Developing Data Products/CrimeUSA')
load("crimeusa.rda")

shinyServer(function(input, output) {
  # decade output
  output$decade=renderText({paste("From ",input$Decade+1,"to ",input$Decade+10)})
  # rCharts
  animateMap <- function (x, data, colors, map = "usa", ...){
    fml = lattice::latticeParseFormula(x, data = data)
    data = transform(data, fillKey = fml$left)
    d <- Datamaps$new()
    d$set(scope = map, fills = as.list(colors), 
          data = dlply(data, fml$right.name), ...)
    return(d)
  }
  output$animatedChart = renderChart({
    animatedChart=animateMap(
      CrimeRate~state,
      data = crimeusa[crimeusa$Year==input$Decade,],
      colors = c("","#4daf4a","#fc8d62","red")
    )
    animatedChart$addParams(dom = 'animatedChart') 
    return(animatedChart)
  })
})
#```

--- .class #id 


## Prepare for Slidify

```{r, eval=FALSE}
## install packages
install.packages("devtools")
library(devtools)

## install slidify
install_github('slidify','ramnathv')
install_github('slidifyLibraries','ramnathv')

## load Slidify
library(slidify)

## set working directory
setwd('~/OneDrive/Radu Craioveanu/School/Data Science at John Hopkins on Coursera/Developing Data Products/CrimeUSA/CrimeUSASlidify')

## create the project 
author("CrimeUSASlidify")
```

--- .class #id 

## Create Slidify Preso 

```{r, eval=FALSE}
## edit index.html created in the working directory ./CrimeUSASlidify

## create the slidify presentation
slidify("index.Rmd") ## or runDeck("index.Rmd")

## browse the preso with your browser
browseURL("index.html")
```




