---
title: "Developing Data Products - Quiz 2"
author: "radu craioveanu"
date: "Sep 12, 2015"
output: html_document
---

```{r, echo=FALSE,include=FALSE}
setwd("~/OneDrive/Radu Craioveanu/School/Data Science at John Hopkins on Coursera/Developing Data Products")
```

```{r Setup the Options for knitr behavior for code chunks,include=FALSE}
require(knitr)
knitr::opts_chunk$set(echo=TRUE,fig.path = './figure/')
```

#Question 1

In the slidify YAML text. Changing the framework from io2012 to shower does what?

It changes the ability to display mathjax javascript rendering.

It changes whether the document is self contained or requires being connected to the internet.

It changes nothing.

###Answer
It changes the html5 framework thus changing the style of the slides.

#Question 2

You wrote R code in a slidify document as follows
```{r, eval=FALSE}
fit <- lm(y ~ x1 + x2 + x3)
summary(fit)
```

If you want to hide the results of the summary statement (yet still have it run) what should you do?

Comment out the command # summary(fit)

###Answer
Add a results = 'hide' option in the {r} call of the code chunk

Add a echo = FALSE option in the {r} call of the code chunk

Comment the command as below but also use a bang symbol after the comment, as in #! summary(fit)

#Question 3
You wrote R code in a slidify document as follows
```{r, eval=FALSE}
fit <- lm(y ~ x1 + x2 + x3)
summary(fit)
```

If you want to display the results, but not the actual code, what should you do?

Comment out the command # summary(fit)

Add a echo = TRUE option in the {r} call of the code chunk

Comment the command, but use a bang symbol after the comment, as in #! summary(fit)

###Answer
Add a echo = FALSE option in the {r} call of the code chunk

#Question 4

R studio presentation tool does what?

Creates a presentation that can only be run from within Rstudio.

Creates presentable R code from within presentations. However, it does not actually run the code.

###Answer
Creates HTML5 slides using a generalized markdown format having an extention Rpres and creates reproducible presentations by embedding and running the R code from within the presentation document.

Creates a power point presentation from a generalized markdown format having an extension Rpres.

#Question 5

In Rstudio presenter, if you do not want the code to be evaluated, what option do you need to add to the {r} options?
```{r, eval=FALSE}
```

echo = FALSE

run = FALSE

results = 'hide'

###Answer
eval = FALSE

#Question 6

When presenting data analysis to a broad audience, which of the following should be done?

Show every analysis and method that was done.

###Answer
Explain why each step was necessary.

Do not include figure captions.

Present results in the chronological order in which it was performed.