---
title: "Developing Data Products - Quiz 3"
author: "radu craioveanu"
date: "Oct 10, 2015"
output: html_document
---

```{r, echo=FALSE,include=FALSE}
setwd("~/OneDrive/Radu Craioveanu/School/Data Science at John Hopkins on Coursera/Developing Data Products")
```

```{r Setup the Options for knitr behavior for code chunks,include=FALSE}
require(knitr)
knitr::opts_chunk$set(echo=TRUE,fig.path = './figure/')
```

#Question 1

Which of the following items is required for an R package to pass R CMD check without any warnings or errors?

example data sets

a demo directory

vignette

##Answer
DESCRIPTION file

#Question 2

Which of the following is a generic function in a fresh installation of R, with only the default packages loaded?

##Answer
show

dgamma

lm

colSums

#Question 3

What function is used to obtain the function body for an S4 method function?

showMethods()

getS3method()

getClass()

##Answer
getMethod()

#Question 4

Which one of the following functions must be defined in order to deploy an R function on yhat?

##Answer
model.predict

model.require

model.transform

model.load

#Question 5

Please download the R package DDPQuiz3 from the course web site. Examine the createmean function implemented in the R/ sub-directory. What is the appropriate text to place above the createmean function for Roxygen2 to create a complete help file?

```{r}
#' This function calculates the mean
#' 
#' @param x is a numeric vector
#' @return the mean of x
#' @export
#' @examples 
#' x <- 1:10
#' createmean(y)
```
```{r}
#' This function calculates the mean
#' 
#' @return the mean of x
#' @export
#' @examples 
#' x <- 1:10
#' createmean(x)
```
```{r}
#' This function calculates the mean
#' 
#' @param x is a numeric vector
#' @export
#' @examples 
#' x <- 1:10
#' createmean(x)
```
##Answer
```{r}
#' This function calculates the mean
#' 
#' @param x is a numeric vector
#' @return the mean of x
#' @export
#' @examples 
#' x <- 1:10
#' createmean(x)
```