---
title: "Developing Data Products - Quiz 1"
author: "radu craioveanu"
date: "Sep 8, 2015"
output: html_document
---

```{r, echo=FALSE,include=FALSE}
setwd("~/OneDrive/Radu Craioveanu/School/Data Science at John Hopkins on Coursera/Developing Data Products")
```

```{r Setup the Options for knitr behavior for code chunks,include=FALSE}
require(knitr)
knitr::opts_chunk$set(echo=TRUE,fig.path = './figure/')
```

#Question 1

Consider the following code for the cars data set

```{r}
library(manipulate)
myPlot <- function(s) {
    plot(cars$dist - mean(cars$dist), cars$speed - mean(cars$speed))
    abline(0, s)
}
```

This function plots distance versus speed, each de-meaned and an associated line of slope s. Which of the following code will make a manipulate plot that creates a slider for the slope?

manipulate(myPlot(s), x.s = slider(0, 2, step = 0.1))

manipulate(myPlot(s), slider = x(0, 2, step = 0.1))

##Answer
manipulate(myPlot(s), s = slider(0, 2, step = 0.1))

manipulate(myPlot, s = slider(0, 2, step = 0.1))

#Question 2

Which of the following code uses the rCharts package to create a sortable and searchable data table for the airquality data set? Assume the rCharts package and the airquality data set have already been loaded into R.

```{r}
require(rCharts)

##Answer
dTable(airquality, sPaginationType = "full_numbers")

d <- data.frame(airquality, stringsAsFactors = FALSE) print(d)

airquality

head(airquality)
```

#Question 3
A basic shiny data product requires:

A shiny.R file.

##Answer
A ui.R and server.R file or a A server.R file and a directory called www containing the relevant html files.

A server.R file only.

A ui.R file only.

#Question 4

What is incorrect about the followig syntax in ui.R?

```{r}
library(shiny)
shinyUI(pageWithSidebar(
  headerPanel("Data science FTW!"),
  sidebarPanel(
    h2('Big text'), ##had to add the comma after this row
    h3('Sidebar')
  ),
  mainPanel(
      h3('Main Panel text')
  )
))
```

The h2 command has the wrong arguments.

##Answer
Missing a comma in the sidebar panel

The h3 command should be an h2 command.

The "Sidebar" should say "Sidebar text".

#Question 5
Consider the following code in ui.R

```{r}
shinyUI(pageWithSidebar(
  headerPanel("Example plot"),
  sidebarPanel(
    sliderInput('mu', 'Guess at the mu',value = 70, min = 60, max = 80, step = 0.05,)
  ),
  mainPanel(
    plotOutput('newHist')
  )
))
```

And the following server.R code.

```{r}
library(UsingR)
data(galton)

shinyServer(
  function(input, output) {
    output$myHist <- renderPlot({ #need to call it newHist
      hist(galton$child, xlab='child height', col='lightblue',main='Histogram')
      mu <- input$mu
      lines(c(mu, mu), c(0, 200),col="red",lwd=5)
      mse <- mean((galton$child - mu)^2)
      text(63, 150, paste("mu = ", mu))
      text(63, 140, paste("MSE = ", round(mse, 2)))
      })
    
  }
)
```


Why isn't it doing what we want?

##Answer
The server.R output name isn't the same as the plotOutput command used in ui.R.

The limits of the slider are set incorrectly and giving an error.

The phrase "Guess at the mu value" should say "mean" instead of "mu"

It should be mu <- input$mean in server.R
